---
title: "Web Scraping Tutorial"
output: html_notebook
---

> This tutorial is from: https://www.freecodecamp.org/news/an-introduction-to-web-scraping-using-r-40284110c848/

> First there are some packages that need to be insttaled first.

```{r}
install.packages("selectr")
install.packages("xml2")
install.packages("rvest")
```

> Some basic web scraping functions include:

+ **read_html(url)**: scrape HTML content from a given URL
+ **html_nodes()**: identifies HTML wrappers.
+ **html_nodes(".class")**: calls node based on CSS class
+ **html_nodes("#id")**: calls node based on '<div>' id
+ **html_nodes(xpath="xpath")**: calls node based xpath (we'll cover this later)
+ **html_attrs()**: identifies attributes (useful for debugging)
+ **html_table()**: turns HTML tables into data frames
+ **html_text()**: strips the HTML tags and extracts only the text

### Stringr

> stringr is used for data cleaning and preparation. There are four functions to stringr

+ functions allow you to work around individual characters within strings
+ whitespace can be manipulated
+ locale sensitive operations
+ pattern matching functions

```{r}
install.packages("stringr")
```

### jsonlite

> This package allows easy conversion between R objects and JSON without loss of type or information. It also allows for easy interaction with APIs

```{r}
install.packages("jsonlite")
```

## Implementation

**Load Packages**

```{r}
library(xml2)
library(rvest)
library(stringr)
```

**Read HTML content from select site**

```{r}
url <- "https://www.amazon.in/OnePlus-Mirror-Black-64GB-Memory/dp/B0756Z43QS?tag=googinhydr18418-21&tag=googinkenshoo-21&ascsubtag=aee9a916-6acd-4409-92ca-3bdbeb549f80"

webpage <- read_html(url)
```

> The webpage elements can be inspected to retreive the class IDs. In this example to retrieve the title the class id is *title*

```{r}
#pull title from site
title_html <- html_nodes(webpage, 'h1#title')
#convert to text
title <- html_text(title_html)

head(title)
```


> Looking at the head file you can see that there are a lot of spaces. To remove them use the code below. 

```{r}
str_replace_all(title, "[\r\n]" , "")
```



